Argennon: A Scalable Cloud Based Smart Contract Platform Using Argument of Knowledge Systems

### 2023-01-11 tex/sections/blocks.tex
Improve readability of "Block Validation" SubSection
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

The Argennon blockchain is a sequence of blocks. Every block represents an ordered list of external requests, intended
to be executed by the Argennon Smart Contract Execution Environment (AscEE). The first block of the blockchain, the
\emph{genesis} block, is a spacial block that fully describes the initial state of the AscEE. Every block of the
Argennon blockchain thus corresponds to a unique AscEE state which can be calculated deterministically from the genesis
block.

@@

\begin{center}
    \begin{tabular}{||c||}
        \hline
        \textbf{Block} \\ [0.6ex]
        \hline\hline
        height: $h$                          \\ [1.2ex]
        commitment to the program database: $\mathbf{C}_{P}$             \\ [1.2ex]
        commitment to the heap database: $\mathbf{C}_{H}$               \\ [1.2ex]
        commitment to the ordered list of requests: $\mathbf{C}_{R}$        \\ [1.2ex]
        clustering directives: $dir$                        \\ [1.2ex]
        certificate of the validator assembly for \\
        the block with height $h - k$: $v \mhyphen cert_{h-k}$         \\ [1.2ex]
        certificate of the delegates for\\
        the previous block: $d \mhyphen cert_{h-1}$        \\ [1.2ex]
        previous block hash                           \\ [1.2ex]
        \hline
    \end{tabular}
\end{center}

To validate a block three main conditions need to be validated: (i) commitments to the program and heap
database are resulted from applying the request list and clustering directives of the block to the previous AscEE
state, (ii) $v \mhyphen cert_{h-k}$ is valid, (iii) previous block is valid and has height $h - 1$.

The Argennon Prover Machine provides a convenient and universal way for arithmetization of any Argennon
application. Moreover, since a compiled version of every Argennon application to the APM code is stored in the AscEE
program area, validators do not need to locally store the APM code of applications.

The Argennon protocol does not enforce the usage of the APM. Validators and PVC servers can use any argument system
with any arithmetization, and if required, the ASAR of an application can be used
for generating the appropriate arithmetization instead of the APM\@.

The certificate of validators, $v \mhyphen cert_{h-k}$, is an aggregate signature. Validating it requires accessing the
AscEE heap state at block $h-k-m$ to obtain public keys and stake values. Here $m$ is the total number of validator
assemblies and $k$ is the maximum allowed length of
the unvalidated chain. (See Section\ref{subsec:validators-committee})
Again, in addition to direct verification, a validator can use computational integrity proofs, received from the
Argennon cloud, to perform cheaper verification of this certificate.

For validating the previous block, instead of directly validating the content of the block, a validator only
verifies the block certificates. Verifying $d \mhyphen cert_{h-1}$ is straightforward. Verifying $v \mhyphen
cert_{h-1}$, which should be performed based on stakes at block $h-m-1$, can be cheaply done by using computational
proofs, obtained from the Argennon cloud.

In summary, a validator validates a block by verifying three computational integrity proofs: $\pi_{\tau}$ which proves
the transition is correct, $\pi_{h-k}$ which proves the validity of the included certificate of block $h-k$ and
$\pi_{h-1}$ which proves the previous block has a correct certificate of validators. It should be noted that these
proofs are not a part of the block contents and therefore the exact argument system used for generating them is not
specified by the Argennon protocol.

@@

\begin{itemize}
    \item $\textbf{KeyGen}()$: choose a random $\alpha$ from $\Z_q$ and set $h \gets g_1^\alpha \in \G_1$.
    output $\PK \deq (h)$ and $\SK \deq (\alpha)$.
    \item $\textbf{Sign}(\SK, m)$: output $\sigma \gets \Hm(m)^\alpha \in \G_0$.
    The signature $\sigma$ is a \emph{single} group element.
    \item $\textbf{Verify}(\PK,m,\sigma)$: if $e(g_1, \sigma) = e\big(\PK,\ \Hm(m)\big)$  then output "accept",
    otherwise output "reject".
\end{itemize}

Given triples $(\PK_i,\ m_i,\ \sigma_i)$ for $i=1,\ldots,n$,
anyone can aggregate the signatures $\sigma_1,\ldots,\sigma_n \in \G_0$
into a short convincing aggregate signature $\sigma$ by computing
\begin{equation}
    \label{eq:agg}
    \sigma \gets \sigma_1 \cdots \sigma_n \in \G_0\ .
\end{equation}
Verifying an aggregate signature $\sigma \in \G_0$ is done by checking that
\begin{equation}
    \label{eq:aggdiff}
    e(g_1, \sigma) = e\big(\PK_1,\ \Hm(m_1)\big) \cdots e\big(\PK_n,\ \Hm(m_n)\big)\ .
\end{equation}
When all the messages are the same ($m = m_1 = \ldots = m_n$), the verification relation~\eqref{eq:aggdiff} reduces to
a simpler test that requires only two pairings:
\begin{equation}
    \label{eq:aggsame}
    e(g_1, \sigma) = e\Big(\PK_1 \cdots \PK_n,\ \Hm(m)\Big)\ .
\end{equation}
We call $\APK=\PK_1 \cdots \PK_n$ the aggregate public key.

@@

>>>>

The Argennon blockchain is a sequence of blocks. Every block represents an ordered list of external requests, intended
to be executed by the Argennon Smart Contract Execution Environment (AscEE). The first block of the blockchain, the
\emph{genesis} block, is a spacial block that fully describes the initial state of the AscEE and every block of the
Argennon blockchain thus corresponds to a unique AscEE state which can be calculated deterministically from the genesis
block.

@@

\begin{center}
    \begin{tabular}{||c||}
        \hline
        \textbf{Block} \\ [0.6ex]
        \hline\hline
        height: $h$                          \\ [1.2ex]
        commitment to the program database: $\mathbf{C}_{P}$             \\ [1.2ex]
        commitment to the heap database: $\mathbf{C}_{H}$               \\ [1.2ex]
        commitment to the ordered list of requests: $\mathbf{C}_{R}$        \\ [1.2ex]
        clustering directives: $dir$                        \\ [1.2ex]
        certificate of the validator assembly for \\
        the block with height $h - k$: $v \mhyphen cert_{h-k}$         \\ [1.2ex]
        previous block hash                           \\ [1.2ex]
        \hline
    \end{tabular}
\end{center}

@@

\begin{itemize}
    \item $\textbf{KeyGen}()$: choose a random $\alpha$ from $\Z_q$ and set $h \gets g_1^\alpha \in \G_1$.
    output $\PK \deq (h)$ and $\SK \deq (\alpha)$.
    \item $\textbf{Sign}(\SK, m)$: output $\sigma \gets \Hm(m)^\alpha \in \G_0$.
    The signature $\sigma$ is a \emph{single} group element.
    \item $\textbf{Verify}(\PK,m,\sigma)$: if $e(g_1, \sigma) = e\big(\PK,\ \Hm(m)\big)$  then output ``accept'',
    otherwise output ``reject''.
\end{itemize}

Given triples $(\PK_i,\ m_i,\ \sigma_i)$ for $i=1,\ldots,n$,
anyone can aggregate the signatures $\sigma_1,\ldots,\sigma_n \in \G_0$
into a short convincing aggregate signature $\sigma$ by computing
\begin{equation}
    \label{eq:agg}
    \sigma \gets \sigma_1 \cdots \sigma_n \in \G_0\ \cdot
\end{equation}
Verifying an aggregate signature $\sigma \in \G_0$ is done by checking that
\begin{equation}
    \label{eq:aggdiff}
    e(g_1, \sigma) = e\big(\PK_1,\ \Hm(m_1)\big) \cdots e\big(\PK_n,\ \Hm(m_n)\big)\ \cdot
\end{equation}
When all the messages are the same ($m = m_1 = \ldots = m_n$), the verification relation~\eqref{eq:aggdiff} reduces to
a simpler test that requires only two pairings:
\begin{equation}
    \label{eq:aggsame}
    e(g_1, \sigma) = e\Big(\PK_1 \cdots \PK_n,\ \Hm(m)\Big)\ \cdot
\end{equation}
We call $\APK=\PK_1 \cdots \PK_n$ the aggregate public key.

@@

To validate a block three main conditions need to be validated: (i) commitments to the program and heap
database are resulted from applying the request list and clustering directives of the block to the previous AscEE
state, (ii) previous block is valid and has height $h - 1$, (iii) $v \mhyphen cert_{h-k}$ is valid.

The Argennon Prover Machine provides a convenient and universal way for arithmetization of any Argennon
application. Moreover, since a compiled version of every Argennon application to the APM code is stored in the AscEE
program area, validators that use the APM do not need to locally store the APM code of applications.

The Argennon protocol does not enforce the usage of the APM. Validators and PVC servers can use any argument system
with any arithmetization, and if required, the ASAR of an application can be used
for generating the appropriate arithmetization instead of the APM arithmetization.

For validating the previous block, instead of directly validating the contents of the block, a validator only
verifies the block certificates. Each block of the Argennon blockchain has two certificates: the certificate of
validators, $v \mhyphen cert$, and the certificate of the delegates, $d \mhyphen cert$. Verifying $d \mhyphen
cert_{h-1}$ is straightforward but verifying $v \mhyphen cert_{h-1}$ is more challenging. $v \mhyphen cert_{h-1}$ is an
aggregate signature and validating it requires accessing the AscEE heap state at block $h-1-m$, where $m$ is the
total number of validator assemblies, to obtain public keys and stake values. Again, in addition to direct
verification, a validator can use computational integrity proofs, received from the Argennon cloud, to perform
cheaper verification of this certificate.

The block at height $h$ includes a certificate of validators for block $h-k$ which is used to record the participation
of validators and facilitate reward calculation. This certificate needs to be validated based on stake and public key
database at block $h-k-m$, and can be cheaply done by using computational proofs, obtained from the Argennon cloud.
Here $k$ is the maximum allowed length of the unvalidated part of the Argennon blockchain. (See
Section~\ref{subsec:validators-committee})

In summary, a validator validates a block by verifying three computational integrity proofs: $\pi_{\tau}$ which proves
the transition is correct, $\pi_{h-1}$ which proves the previous block has a correct certificate of validators and
$\pi_{h-k}$ which proves the validity of the included certificate of validators of block $h-k$. It should be noted that
these proofs are not part of the block contents and therefore the exact argument system used for generating them is
not specified by the Argennon protocol.

### 2023-01-11 tex/sections/concurrency.tex
Improve readability of "Block Validation" SubSection
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

Every block of the Argennon blockchain contains a list of transactions. This list is an ordered list and the
effect of its contained transactions must be applied to the AscEE state sequentially as they appear in the ordered
list. This ordering is solely chosen by the block proposer, and users should not have any assumptions about
the ordering of transactions in a block.

The fact that block transactions constitute a sequential list, does not mean they can not be executed and applied
to the AscEE state concurrently. Many transactions are actually independent and the order of their execution does not
matter. These transactions can be safely validated in parallel by validators.

>>>>

Every block of the Argennon blockchain contains a list of transactions. This list is an ordered list and the
effect of its contained transactions must be applied to the AscEE state sequentially as they appear in the ordered
list.\footnote{This ordering is solely chosen by the block proposer, and users should not have any assumptions about
the ordering of transactions in a block.}

The fact that block transactions constitute a sequential list, does not imply they can not be executed and applied
to the AscEE state concurrently. Many transactions are actually independent and the order of their execution does not
matter. These transactions can be safely validated in parallel by validators.
